\section{Miscellaneous}

\subsection{Press and Media}

\miscentry{2024}{The Register}{
  \textit{Lab-grown human brain cells drive virtual butterfly in simulation.} \href{https://www.theregister.com/2024/10/22/human_brain_tissue_butterfly_simulation}{Link to article}}{Article}{
  News article in The Register featuring the FinalSpark Butterfly project, based on an interview.
}
\miscentry{2024}{Tom’s Hardware}{\textit{World’s first bioprocessor uses 16 human brain organoids for a million times less power consumption than a digital chip.} \href{https://www.tomshardware.com/pc-components/cpus/worlds-first-bioprocessor-uses-16-human-brain-organoids-for-a-million-times-less-power-consumption-than-a-digital-chip}{Link to article}
}{Article}{
  Article in Tom’s Hardware about the FinalSpark Neuroplatform, achieving significant global attention with millions of views on social media and numerous inquiries.
}
\miscentry{2024}{YouTube}{
  \textit{Demo showcase: Lab-Grown Human Brain Living in a Virtual World.} \href{https://youtu.be/32qlv6dKILQ?si=63N-0bF7U4HTIw6S}{Link to video}}{Video}{
  Trailer video I created and uploaded showcasing the Neuroplatform project. Achieved over 120,000 views, 1,000+ comments, and contributed to 1,000+ new subscribers on my YouTube channel.
}
\miscentry{2024}{Short Film}{
  \textit{Astral Journey.} \href{https://youtu.be/mnKc3mdMa2E?si=D3xH5R_-L65N1svA}{Link to trailer}}{Trailer}{
  Sci-fi short film where I served as an advisor to the filmmaker on concepts related to consciousness, mind-uploading, and whole brain emulation. The film is currently being presented at film festivals.
}
\miscentry{2023}{YouTube}{
  \textit{Explainer: What is a Neural/Cloud Interface?} \href{https://youtu.be/nJGVc9eDGmg?si=e7VrnEp7Zu0J5EiP}{Link to video}}{Video}{
  Explainer video I scripted and created (including motion graphics) about neural/cloud interfaces, based on my research at IDUN Technologies.
}

\subsection{Memberships and Partnerships}

% TODO Add this item as well
% UCL's TeQ, or Surgical Technology at Queen Square Group, focuses on enhancing neurosurgical patient outcomes through the integration of advanced surgical technologies. The group comprises a multidisciplinary team of clinicians, engineers, and students, dedicated to research and development in surgical practices. Their projects include assessing the learning curves associated with high-volume simulation training for surgical procedures.

% TODO Add this item as well
% Infinita in Prospera on the island of Roatan.
% Protocol Labs for the Future (maybe Solana and Polygon collabs as well)
% Cellink (or some other bio-printing company)
% FinalSpark/CorticalLabs (or some other neuro-platform company)

\miscentry{2024+}{Nervana}{Community Member}{}{
  Active participant in a UK-based community of neurosurgeons and neurotechnologists, engaging in monthly discussions on current neurosurgery paper reviews and journal clubs.
}
\miscentry{2023+}{BCI Society}{General Member}{}{
  General member of the BCI Society, an organisation dedicated to the development of brain-computer interface research.
}
\miscentry{2022+}{NeuroTechX}{Member and Advocate}{}{
  Member of NeuroTechX, an organisation and community with the aim to build and advance neurotech.
}

\subsection{Supplementary Training}
\miscentry{2024}{3D Printing and Biofabrication}{Utrecht University}{Summer School}{
  Intensive summer course focused on the applications of 3D printing in biofabrication and tissue engineering at the Utrecht Medical Center.
}
\miscentry{2024}{Neuronal Dynamics by Prof. Gerstner Wulfram}{EPFL Lausanne}{Extra Lectures}{
  Participation in extra lectures on neuronal dynamics by Prof. Gerstner Wulfram, enhancing understanding of mathematical neuroscience.
}
\miscentry{2024}{Systems Neuroscience by Prof. Mathis Mackenzie}{EPFL Lausanne}{Extra Lectures}{
  Engagement with advanced concepts in systems neuroscience from Prof. Mathis Mackenzie, deepening insights into neural networks and deep learning.
}
\miscentry{2022}{Applied Machine Learning}{Constructor Academy}{Online Bootcamp}{
  Intensive online bootcamp focused on practical machine learning techniques, covering various applications and algorithms.
}
\miscentry{2019}{Games Programming}{SAE Institute Frankfurt}{Extra lectures}{
  Attendance of extra lectures focusing on the practicalities of programming games in game engines such as Unity 3D and Unreal Engine.
}
\miscentry{2018}{Game Design}{SAE Institute Zürich}{Extra lectures}{
  Attendance of extra lectures focusing on game design practices with Autodesk Maya and ZBrush.
}
\miscentry{2017}{3D Design}{School of Design Bern and Biel}{Evening Course}{
  Evening course focused on developing foundational skills in 3D design principles and software with Cinema 4D.
}

\subsection{Services}
\miscentry{year-now}{Label}{Title}{Address}{
  Description
}

\subsection{Side Projects}
\miscentry{year-year}{Label}{Title}{Address}{
  Description
}

% TODO: Add links to the online platforms
\subsection{Hobbies}
% \miscentry{2020+}{Programming Leaderboard}{35+ weekly hours}{Wakatime.com}{
%   I have been programming regularly since 2020, averaging over 35 hours per week.
% }

\miscentry{2023+}{Online Chess}{1200+ peak ELO}{Chess.com}{
  I play online chess occasionally (averaging 15+ daily games) and have achieved a peak rating of over 1200 ELO on Chess.com. I also participate in some long-running games to relax my mind.
}

% \miscentry{2022+}{Online Language Learning}{1000+ days streak}{Duolingo}{
%   Learning 5 languages at the same time, with a streak of over 1000 days.
% }