\section{Projects}

\subsection{Active Projects}

\researchentry{Augmented Progressive Brain Replacement}{Eightsix Science}{Reconstruction Pipeline, Surgical Procedure, Virtual World}{August 2024 – present}{
  \item Developing a patient-specific 3D-bioprinted neural graft procedure for seamless replacement of aged, damaged, and silenced brain tissue, focusing on cognitive continuity. \textbf{This effort aims to facilitate neural regeneration/replacement and, by that, eliminate most neurodegenerative diseases.}
}

\researchentry{Ectopic Cognitive Preservation}{Eightsix Science}{Brain Explantation, Perfusion System, Biohybrid Brain-Computer Interface}{August 2024 – present}{
  \item Designing technologies for long-term maintenance of a human brain outside the body using a large-scale perfusion system and simulated sensory input via a novel brain-computer interface. \textbf{This effort aims to overcome ageing as a disease, and potentially extend lifespans indefinitely.}
}

\subsection{Previous Involvements}

\researchentry{Neuroplatform: \url{https://finalspark.com/neuroplatform}}{FinalSpark}{Neuroplatform SDK, Neuroplatform API, FinalSpark Butterfly Demo}{August 2023 – October 2024}{
  \item Co-created a cloud platform enabling real-time interaction between human brain organoids in virtual environments, showcasing their unique learning capabilities. \textbf{This research aims to enable organoid intelligence: a supercomputer running on just 20 watts with true general intelligence.}
}

\researchentry{Blue Brain Project: \url{https://www.epfl.ch/research/domains/bluebrain}}{EPFL}{Blue Brain Nexus, NeuroMorphoVis, Open Brain Institute Platform}{November 2023 – July 2024}{
  \item Contributed to digital brain reconstruction and simulation, enhancing Blue Brain Nexus and developing the Open Brain Platform for accessible brain simulations. \textbf{This enables easy access to virtual wet labs, reducing animal-based experiments and accelerating neuroscientific understanding.}
}

\researchentry{IDUN Guardian: \url{https://iduntechnologies.com/idun-guardian}}{IDUN Technologies}{Guardian Console, Guardian SDKs, Guardian Cloud, Guardian Dev Docs}{October 2021 – July 2023}{
  \item Co-built IDUN Technology’s neurointelligence platform, converting brain signals from in-ear EEG hardware into actionable insights via a cloud-based system, companion apps, and SDKs. \textbf{This aims to democratise access to brain-computer interface technology by integrating it into everyday consumer earbuds, making the brain accessible through a secure API.}
}

\researchentry{Hexagon HxDR: \url{https://hxdr.com}}{Hexagon}{HxDR Cloud, HxDR Web, HxDR Gateway, HxDR SDK}{March 2021 – September 2021}{
  \item Contributed to Hexagon’s cloud-based HxDR platform for storage, visualisation, and collaboration, enabling the capture and management of high-resolution geospatial data and digital twins. \textbf{This work enables real-time simulations and management of digital reconstructions of the entire world, providing invaluable data for infrastructure planning, disaster response (e.g., flooding and storm simulations), and urban development (e.g., 5G tower placement), which were previously impossible.}
}