\section{Publications}

\subsection{Journal Papers}

\publications{
  Jordan, F. D., Kutter, M., Comby, J., Brozzi, F., \& Kurtys, E. (2024). \emph{Open and remotely accessible Neuroplatform for research in wetware computing}. A paper exploring the design and development of a novel platform for brain-computer interface research. Frontiers in Artificial Intelligence, \url{https://doi.org/10.3389/frai.2024.1376042} (\textbf{Burger, D.}, Minor Author)
}

\subsection{Patents}
\publications{
  \textbf{Burger, D.}, Gisin, S., Bachmann, S., Thielen, M. (2022). EP4369655A1 – \emph{System and method for secure handling of sensitive data} – A patent focused on secure data management and transmission. Google Patents. \url{https://patents.google.com/patent/EP4369655A1}
}

\subsection{Posters and Presentations}
\publications{
  List of posters and other presentations at conferences or seminars.
}

\subsection{Preprints and in Progress}
\publications{
  \textbf{Burger, D.}, Watanabe, M., Cunha, G., \& Hande, I. (In preparation, targeting 2025). \emph{Biohybrid-first approaches to mind-uploading within the next 20 years} (Working title).

  Koene, R., \textbf{Burger, D.} et al. (In preparation). \emph{Whole brain emulation roadmap 2.0} (Contributing Author). An updated comprehensive guide to whole brain emulation, building upon the foundational work of Nick Bostrom and Anders Sandberg: \url{http://www.fhi.ox.ac.uk/reports/2008-3.pdf}
}

\subsection{Online Publications and Essays}
\publications{
  \textbf{Burger, D.} (2024). \emph{Lab-Grown Human Brain Embodied in a Virtual World}. Daniel Burger’s Substack. \url{https://danburonline.substack.com/p/lab-grown-brain-embodied-in-vr}

  \textbf{Burger, D.} (2023). \emph{The Influence of Brain-Computer Interfaces on the World Wide Web}. Nerd For Tech. \url{https://medium.com/p/f93a329816cd}
}

\subsection{Other Contributions}
\publications{
  White, E. J. B. (2024). \emph{\underbar{Book:} AI Today: OI Tomorrow: The Dawn of Organoid Intelligence}. Packt Publishing. \url{https://www.amazon.com/dp/B0D2Z24L2L} (\textbf{Burger, D.}, Advisor)

  \textbf{Burger, D.} (2023). \emph{\underbar{Middlesex University Bachelor’s thesis:} Enabling General Applicability for Brain-Computer Interface Software Through Cloud Computing}. ResearchGate. \url{https://doi.org/10.13140/RG.2.2.34970.21442}
}